Manuscript

### 2025-03-06 Manuscript_MD_ScoreReLiability.qmd
fix direction in scripts

Therefore, in the following section we assess to what extent this
intuition can be . The re-analysis of archival data is

@@

We have attempted to collect all openly available multi-site direct
replications on psychological phenomena (Fünderich et al. 2024). The
data-sets of about 50 phenomena , largely stemming from the efforts of
the Many Labs studies, Registered Replication Reports or the
Psychological Science Accelerator, are made openly available in a
standardised format at \[osf.io\], the DRIPHT repository.

@@

From the 22 phenomena that employed more than a single indicator, 19
made use of Likert-style items, where respondents would indicate their
agreement to some kind of statement. The scale-length varied from 3 to
10-points. The items measuring the remaining 3 phenomena were coded
dichotomously, as responses were right or wrong (2 cases), or expressed
agreement vs disagreement dichotomously (1 case). While the majority of
designs make use of some form of control-treatment manipulation,
randomly assigning participants to a condition (20 phenomena), some
phenomena discuss the effect of pre-existing differences, e.g.
biological sex (2 phenomena). Subsequently, those phenomena need to be
identified where the meta-analytic mean effect size is statistically
significant different from zero. This will be done as a first step of
this manuscript’s analysis procedure. Detailed information concerning
the different phenomena and how they were measured can be found at
\[osf-link\], while a brief summary can be found in Table 1.

@@

For each replication of a phenomenon, Cohen’s $d$ is computed as an
estimate of raw ES, according to @eq-d, including its standard error
(@eq-SEd). Subsequently, a random-effects meta-analysis is performed
using metafor version X.XX. To estimate meta-analytic mean ES and
heterogeneity, the REML-estimator is used (ref). To identify which
phenomena pass criterion (3), using a Wald-type significance test we
assess for which phenomenon the meta-analytic mean ES is significantly
different from zero. For this hypothesis test, as all other hypothesis
tests in this manuscript, a significance level of .05 is used.

>>>>

Therefore, in the following section we assess to what extent this
intuition is supported by empirical evidence. The re-analysis of
archival data serves to shed light on the following two research
questions central to this text:

-   Can score reliability be used to explain heterogeneity in
    standardized effect sizes?

-   How does score reliability affect ES heterogeneity?

@@

We have collected a large number of openly available multi-site direct
replications on psychological phenomena (Fünderich et al. 2024). The
data-sets of about 50 phenomena , largely stemming from the efforts of
the Many Labs studies, Registered Replication Reports or the
Psychological Science Accelerator, are made openly available in a
standardised format at \[osf.io\], the DRIPHT repository.

@@

From the 22 phenomena that employed more than a single indicator, 19
made use of Likert-style items, where respondents would indicate their
agreement to some kind of statement. The scale-length varied from 3 to
10-points. The items measuring the remaining 3 phenomena were coded
dichotomously, as responses were right or wrong (2 cases), or expressed
agreement vs disagreement dichotomously (1 case). While the majority of
designs make use of some form of control-treatment manipulation,
randomly assigning participants to a condition (20 phenomena), some
phenomena refer to the effect of pre-existing differences, e.g.
biological sex (2 phenomena). Subsequently, those phenomena need to be
identified where the meta-analytic mean effect size is statistically
significant different from zero. This will be done as a first step of
this manuscript’s analysis procedure. Detailed information concerning
the different phenomena and how they were measured can be found at
\[osf-link\], while a brief summary can be found in Table 1.

@@

For each replication of a phenomenon, Cohen’s $d$ is computed as an
estimate of raw ES, according to @eq-d, including its standard error
(@eq-SEd). Subsequently, a random-effects meta-analysis is performed
using metafor version X.XX. To estimate meta-analytic mean ES and
heterogeneity, the REML-estimator is used (ref). To identify which
phenomena pass criterion (3), using a Wald-type significance test we
assess for which phenomenon the meta-analytic mean ES is significantly
different from zero. For this hypothesis test, as all other hypothesis
tests in this manuscript, a one-tailed significance level of .05 is
used.
